---
title: "Measures and Descriptive Statistics"
output: pdf_document
---

title             : "PSY/SDS 364: Measures and Descriptive Statistics"
shorttitle        : "Measures and Descriptive Statistics"

author: 
  - name          : "Margret Perry"
    affiliation   : "1"
  - name          : "Callie Selvin"
    affliation    : "2"
  - name          : "Isabel Zamudio-Moore"
    affliation    : "3"
  
    corresponding : yes    # Define only one corresponding author
    address       : "Northampton, MA"
    email         : "meperry@smith.edu | cslevin@smith.edu | izamudiomoore@smith.edu"

affiliation:
  - id            : "1"
    institution   : "Smith College"

author_note: >
  Smith College
  
keywords          : "Division of Labor”, Gender Role Development”, “Preschool Activities Inventory", “Gendered Type Play”
wordcount         : "X"

bibliography      : ["references.bib","r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---



```{r include = FALSE}
library(papaja)
#install.packages("psych")
#install.packages("plyr")
library(psysds364data)
library(psych)
library(devtools)
library(tidyr)
library(mosaic)
library(dplyr)
library(ggplot2)
library(plyr)
```

``` {r create_r-references}
r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "r-references.bib")

```








\newpage

# References


\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
