---
title: "Restructing data"
author: "Margaret"
date: "October 23, 2019"
output: pdf_document
---

```{r}
#install.packages("psych")
#install.packages("plyr")
library(psysds364data)
library(psych)
library(devtools)
library(tidyr)
library(mosaic)
library(dplyr)
library(ggplot2)
library(plyr)
```


```{r}
#Call data
data("Goldberg_callie")

##sample code referance
attributes(Goldberg_callie$w16activ4_2)
names(select(Goldberg_callie, contains("age")))
?Goldberg
attributes(Goldberg_callie$w14HHT10_1)
cortest<-corr.test(select(Goldberg_callie, w16activ1_2, w16activ2_2, w16activ3_2,w16activ4_2, w16activ5_2, w16activ6_2, w16activ7_2, w16activ8_2,w16activ9_2, w16activ10_2, w16activ11_2))$r
#names(select(Goldberg_callie, contains("gender")))

attributes(Goldberg_callie$w16activ10_2)
attributes(Goldberg_callie$w16activ3_2)

?Goldberg

```


```{r}
 ggplot(Goldberg_callie, aes(x=sexor))+
    geom_bar()+
   labs(main="Number of Lesbian, Gay, and Heterosexual Couples", x= "Sexual Orientation", y= "Number Of Couples")+
scale_x_discrete(limits=c("Same-Sex","Heterosexual"))
```


# Suggested Variable Select
```{r}
dataSelect<- Goldberg_callie%>%
  select(famid, sexor, gender_1, gender_2,  contains("gender"), contains("w16toys"), contains("14hht"), contains("14chcare"),w14CBCLrace_1,w14CBCLrace_2,  contains("w12Gay"), contains("edu"), w11FamInc_1,  contains("activ16"), contains("LGBTCI"), contains("w14CBCLrace_1"))


```


```{r}
GoldbergCallieFiltered<- dataSelect2%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2))

  
  
  
  
GoldbergCallieFiltered<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) , !is.na(w16toys5_2), !is.na(w14HHT1_1), !is.na(w14HHT2_1) , !is.na(w14HHT3_1), !is.na(w14HHT4_2),!is.na(w14HHT5_1),!is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1), !is.na(w14HHT9_1), !is.na(w14HHT10_1), !is.na(w14HHT11_1), !is.na(w14HHT12_1),!is.na(w14HHT13_1),!is.na(w14HHT1_2), !is.na(w14HHT3_2), !is.na(w14HHT4_2), !is.na(w14HHT5_2),!is.na(w14HHT6_2),!is.na(w14HHT7_2), !is.na(w14HHT8_2), !is.na(w14HHT9_2), !is.na(w14HHT10_2), !is.na(w14HHT11_2), !is.na(w14HHT12_2), !is.na(w14HHT13_2),
   !is.na(w16activ1_1),!is.na(w16activ2_1),!is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1),!is.na(w16activ10_1), !is.na(w16activ11_1),
   !is.na(w16activ1_2),!is.na(w16activ2_1), !is.na(w16activ3_2),!is.na(w16activ4_2), !is.na(w16activ5_2),!is.na(w16activ6_2), !is.na(w16activ7_2),!is.na(w16activ8_2), !is.na(w16activ9_2), 
   !is.na(w16charac1_1), !is.na(w16charac2_1), !is.na(w16charac3_1),!is.na(w16charac4_1), !is.na(w16charac5_1), !is.na(w16charac6_1), !is.na(w16charac1_2), !is.na(w16charac2_2),!is.na(w16charac3_2),!is.na(w16charac4_2),!is.na(w16charac5_2), !is.na(w16charac6_2)
   )

  filter(!is.na(famid), !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) , !is.na(w16toys5_2), !is.na(w16activ1_1),!is.na(w16activ2_1),!is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1))

GoldbergCallieFiltered_1<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) , !is.na(w16toys5_2), !is.na(w16activ1_1),!is.na(w16activ2_1),!is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1), !is.na(w14HHT1_1), !is.na(w14HHT2_1), !is.na(w14HHT3_1),!is.na(w14HHT4_1), !is.na(w14HHT5_1), !is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1),!is.na(w14HHT9_1), !is.na(w14HHT10_1),!is.na(w14HHT11_1), !is.na(w14HHT12_1), !is.na(w14HHT13_1))

```


```{r}

ParCount<- NROW(GoldbergCallieFiltered)
```
#Get Demagraphics for 

```{r}
##Demographic data attributes (gender, sexual orentation, regilion)
attributes(Goldberg_callie$gender_1)
attributes(Goldberg_callie$w14CBCLgender_1)

attributes(Goldberg_callie$w14chgender_2)

attributes(Goldberg_callie$w14Religion_1)

attributes(Goldberg_callie$sexor)
attributes(Goldberg_callie$w14CBCLage_1)
attributes(Goldberg_callie$w14AdSex_2)

##The occurances of demographic varibles
head(Goldberg_callie)
count(Goldberg_callie, vars= "w14Religion_1")
count(Goldberg_callie, vars= "sexor")
count(Goldberg_callie, vars= "gender_1")
count(Goldberg_callie, vars= "w14CBCLgender_1") 
count(GoldbergCallieFiltered, vars= "w14CBCLgender_1") 


### same freq as w14CBCLgender_2 and quest: there is no documentation for what 3,5, and 22 mean
names(Goldberg, select(contains("age")))

count(hetero_gb, vars = "famid")
#sexor based datasets
samesex_gb<- GoldbergCallieFiltered%>%
  filter(sexor == 1)

count(samesex_gb, vars= "w14Religion_1")
count(samesex_gb, vars= "sexor")
count(samesex_gb, vars= "gender_1")
count(samesex_gb, vars= "w14AdSex_1")
count(samesex_gb, vars= "w14CBCLgender_1") 

hetero_gb<- Goldberg_callie%>%
  filter(sexor == -1)

count(hetero_gb, vars= "w14Religion_1")
count(hetero_gb, vars= "sexor")
count(hetero_gb, vars= "gender_1")
count(hetero_gb, vars= "w14AdSex_1")
count(hetero_gb, vars= "w14CBCLgender_1") 


```

```{r}
# Race
attributes(Goldberg_callie$w11Race_2)
attributes(Goldberg_callie$w14CBCLrace_1)
# Income
#Education
count(samesex_gb, vars= "w14CBCLage_1")
is.numeric(samesex_gb$w14CBCLage_1)
ssavg_chage<- mean(samesex_gb$w14CBCLage_1, na.rm= TRUE)

hetero_gb<- GoldbergCallieFiltered%>%
  filter(sexor == -1)

count(hetero_gb, vars= "w14Religion_1")
count(hetero_gb, vars= "sexor")
count(hetero_gb, vars= "gender_1")
count(hetero_gb, vars= "w14AdSex_1")
count(hetero_gb, vars= "w14CBCLgender_1") 
count(hetero_gb, vars= "w14CBCLage_1")
havg_chage<- mean(hetero_gb$w14CBCLage_1, na.rm= TRUE)
```


```{r}
library(papaja)
install.packages("apaTables")
library(apaTables)
install.packages("beeswarm")
library(beeswarm)

# DOES NOT WORK
# apa_table(GoldbergCallieFiltered, aglin = c("Family Income", "Parent Education", "Parent Race", "Girls (%, n)", "Boys (%, n)", "Average Age of Child in Years"), col_spanners = list( c("Homosexual couples" = c(1,2), "Heterosexual Couples" = 3)))

apa_beeplot(
  data = GoldbergCallieFiltered,
  id = "famid",
  dv= "w14CBCLage_1",
  factors = "sexor"
)

apa_beeplot(
  data = GoldbergCallieFiltered,
  id = "famid",
  dv= "w11FamInc_1",
  factors = "sexor"
)


```



```{r}
# Demagraphics on 'child's Race
attributes(GoldbergCallieFiltered$w14CBCLrace_1)

count(GoldbergCallieFiltered, var="w14CBCLrace_1")

```






In our data set we have 
```{r}

#  Demagraphics on Family Income
attributes(GoldbergCallieFiltered$w11FamInc_1)
summary(GoldbergCallieFiltered$w11FamInc_1 )

```

The study had a wide range of family income distribution. With a median of $118,250 earned by a family per year.

```{r}
ggplot(Goldberg_callie, aes(x=w11FamInc_1))+
  geom_histogram()+
  labs(y="Number of Families", x="Household Income")


```




```{r}
#Eucation
attributes(GoldbergCallieFiltered$w11Educ_1)
attributes(GoldbergCallieFiltered$w11Educ_2)

count(GoldbergCallieFiltered, var="w11Educ_1")
count(GoldbergCallieFiltered, var="w11Educ_2")


```
For distribution of eduction it was found that 44 particpants had less than high school for education, 30 had a high school diploma or higher.

```{r}
CollegePlus_1<- GoldbergCallieFiltered%>%
  filter(w11Educ_1!=1,w11Educ_1!=2)

CollegePlus_2<- GoldbergCallieFiltered%>%
  filter(w11Educ_2!=1,w11Educ_2!=2)

```


```{r}
count(Goldberg_callie,var="CollegePlus_1" )
count(Goldberg_callie,var="CollegePlus_2" )

```

* Coincidental?

```{r}


```


```{r}
# Race
attributes(GoldbergCallieFiltered$w11Race_2)
attributes(GoldbergCallieFiltered$w14CBCLrace_1)

count(Goldberg_callie, var="w11Race_2")
count(Goldberg_callie, var="w14CBCLrace_1")


# Income
attributes(Goldberg_callie$w11FamInc_1)
summary(GoldbergCallieFiltered$w11FamInc_1 )

#Eucation
attributes(GoldbergCallieFiltered$w11Educ_1)
attributes(GoldbergCallieFiltered$w11Educ_2)

count(GoldbergCallieFiltered, var="w11Educ_1")
count(GoldbergCallieFiltered, var="w11Educ_2")
attributes(Goldberg_callie$w11Race_2)
attributes(Goldberg_callie$w14CBCLrace_1)

```


```{r}


attributes(Goldberg_callie$w11Race_2)
attributes(Goldberg_callie$w14CBCLrace_1)

Goldberg_callieViewable2<- Goldberg_callie2%>%
  select(w11FamInc)
View(Goldberg_callie2)

```


For the study, our sample size includes 
```{r}
attributes(Goldberg_callie2$w11FamInc)
attributes(Goldberg_callie$w11FamInc_1)
count(Goldberg_callie2, var="w11FamInc")
count(Goldberg_callie, var="w11FamInc_1")
#ggplot(Goldberg_callie2, aes(x= w11FamInc))+geom_histogram()

summary(Goldberg_callie2$w11FamInc)

```



```{r}
FamIncome<- Goldberg_callie%>%
  filter(w11FamInc)
count(Goldberg_callie2, var="w11FamInc")


```


```{r}

FamInc<- Goldberg_callie%>%
  mutate(ww11FamInc=as.integer(w11FamInc_1))%>%
mutate( w11FamInc= ifelse(w11FamInc_1 %in% 0:20000, "20k or less", ifelse(w11FamInc_1 %in% 20001:40000, "20k-40k", ifelse(w11FamInc_1 %in% 40001:60000, "40k-60k", ifelse(w11FamInc_1 %in% 60001:80000, "60k-80k", ifelse(w11FamInc_1 %in% 80001:100000, "80k-100k", ifelse(w11FamInc_1 %in% 100001:730000, "10000k+", "NA" )))))))



```
```{r}
w11FamInc<- Goldberg_callie2%>%
  select(w11FamInc)
View(w11FamInc)
```



#Create a dataframe for Goldberge Callie



```{r}
FamIncome= apply_labels(w11FamInc, w11FamInc= "Family Income")


cro(w11FamInc$w11FamInc,list(total()))

```

The study included data from 223 families that made $100,000 or more while 




```{r}
GoldbergCallieFiltered<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) , !is.na(w16toys5_2), !is.na(w14HHT1_1), !is.na(w14HHT2_1) , !is.na(w14HHT3_1), !is.na(w14HHT4_2),!is.na(w14HHT5_1),!is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1), !is.na(w14HHT9_1), !is.na(w14HHT10_1), !is.na(w14HHT11_1), !is.na(w14HHT12_1),!is.na(w14HHT13_1),!is.na(w14HHT1_2), !is.na(w14HHT3_2), !is.na(w14HHT4_2), !is.na(w14HHT5_2),!is.na(w14HHT6_2),!is.na(w14HHT7_2), !is.na(w14HHT8_2), !is.na(w14HHT9_2), !is.na(w14HHT10_2), !is.na(w14HHT11_2), !is.na(w14HHT12_2), !is.na(w14HHT13_2),
   !is.na(w16activ1_1),!is.na(w16activ2_1),!is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1),!is.na(w16activ10_1), !is.na(w16activ11_1),
   !is.na(w16activ1_2),!is.na(w16activ2_1), !is.na(w16activ3_2),!is.na(w16activ4_2), !is.na(w16activ5_2),!is.na(w16activ6_2), !is.na(w16activ7_2),!is.na(w16activ8_2), !is.na(w16activ9_2), 
   !is.na(w16charac1_1), !is.na(w16charac2_1), !is.na(w16charac3_1),!is.na(w16charac4_1), !is.na(w16charac5_1), !is.na(w16charac6_1), !is.na(w16charac1_2), !is.na(w16charac2_2),!is.na(w16charac3_2),!is.na(w16charac4_2),!is.na(w16charac5_2), !is.na(w16charac6_2)
   )


```


```{r}

ParCount<- NROW(GoldbergCallieFiltered)
ParCount
```

```{r}


goldberg_psai<- Goldberg_callie %>%
  select(w16activ1_1, w16activ2_1, w16activ3_1,w16activ4_1, w16activ5_1, w16activ6_1, w16activ7_1, w16activ8_1,w16activ9_1, w16activ10_1, w16activ11_1, w16toys1_1, w16toys2_1, w16toys3_1, w16toys4_1, w16toys5_1, w16toys6_1, w16toys7_1, w16charac1_1, w16charac2_1, w16charac3_1, w16charac4_1, w16charac5_1, w16charac6_1) %>%
  
  mutate(w16rt2= 6- w16toys2_1,w16rt4 = 6- w16toys4_1, w16rt7 = 6- w16toys7_1,w16ra1 = 6- w16activ1_1, w16ra2 = 6- w16activ2_1, w16ra3 = 6- w16activ3_1, w16ra6 = 6- w16activ6_1, w16ra9 = 6- w16activ9_1, w16ra11 = 6- w16activ11_1,w16rc4 = 6- w16charac4_1,w16rc5 = 6- w16charac5_1,w16rc6 = 6- w16charac6_1)

psai_alpha <- goldberg_psai %>%
  select(w16rt2, w16rt4, w16rt7, w16ra1, w16ra2, w16ra3, w16ra6, w16ra9, w16ra11, w16rc4, w16rc5, w16rc6, w16charac1_1, w16charac2_1, w16charac3_1, w16toys1_1, w16toys3_1, w16toys5_1, w16toys6_1, w16activ4_1, w16activ5_1, w16activ7_1, w16activ8_1, w16activ10_1)

psai_alpha_0 <- psai_alpha %>%
  mutate(pai= round((w16rt2+ w16rt4+ w16rt7 + w16ra1 + w16ra2 + w16ra3 + w16ra6 + w16ra9 + w16ra11 + w16rc4 + w16rc5 + w16rc6 + w16charac1_1+ w16charac2_1+ w16charac3_1+ w16toys1_1+ w16toys3_1 + w16toys5_1+ w16toys6_1+ w16activ4_1+ w16activ5_1+ w16activ7_1+ w16activ8_1+ w16activ10_1) /23))

#cronbach(psai_alpha)


goldberg_hw<- GoldbergCallieFiltered%>%
  select(w14HHT1_1:w14HHT13_1)
hw<- corr.test(goldberg_hw)$r
hw
hw_a<- alpha(hw)
cronbach(goldberg_hw)
```


```{r include = FALSE}
GoldbergCallieFiltered<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), 
!is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) ,
!is.na(w14HHT1_1), !is.na(w14HHT2_1) , !is.na(w14HHT3_1), !is.na(w14HHT4_1), !is.na(w14HHT5_1), !is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1), !is.na(w14HHT9_1), !is.na(w14HHT10_1), !is.na(w14HHT11_1), !is.na(w14HHT12_1), !is.na(w14HHT13_1),
!is.na(w14HHT1_2), !is.na(w14HHT2_2), !is.na(w14HHT3_2), !is.na(w14HHT4_2), !is.na(w14HHT5_2),!is.na(w14HHT6_2), !is.na(w14HHT7_2), !is.na(w14HHT8_2), !is.na(w14HHT9_2), !is.na(w14HHT10_2), !is.na(w14HHT11_2), !is.na(w14HHT12_2), !is.na(w14HHT13_2), 
!is.na(w16activ1_1), !is.na(w16activ2_1), !is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1), !is.na(w16activ10_1), !is.na(w16activ11_1),
!is.na(w16activ1_2), !is.na(w16activ2_2), !is.na(w16activ3_2), !is.na(w16activ4_2), !is.na(w16activ5_2), !is.na(w16activ6_2), !is.na(w16activ7_2), !is.na(w16activ8_2), !is.na(w16activ9_2), !is.na(w16activ10_2),
!is.na(w16activ11_2),
!is.na(w16charac1_1), !is.na(w16charac2_1), !is.na(w16charac3_1), !is.na(w16charac4_1), !is.na(w16charac5_1), !is.na(w16charac6_1), 
!is.na(w16charac1_2), !is.na(w16charac2_2), !is.na(w16charac3_2), !is.na(w16charac4_2), !is.na(w16charac5_2), !is.na(w16charac6_2)
   )

```


```{r}
GoldbergCallieFiltered_CH<-GoldbergCallieFiltered

```

```{r} 
  GoldbergCallieFiltered_CH$w14chcare1_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare1_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare1_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare1_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare1_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare1_1==5,5, 88)))))
summary(GoldbergCallieFiltered_CH$w14chcare1_1)

GoldbergCallieFiltered_CH$w14chcare2_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare1_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare1_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare1_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare1_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare1_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_CH$w14chcare2_2)


```

```{r} 
  GoldbergCallieFiltered_CH$w14chcare2_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare2_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare2_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare2_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare2_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare2_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare2_1)

GoldbergCallieFiltered_HT$w14chcare2_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare2_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare2_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare2_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare2_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare2_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare2_2)

```


```{r} 
  GoldbergCallieFiltered_HT$w14chcare3_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare3_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare3_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare3_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare3_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare3_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare3_1)

GoldbergCallieFiltered_HT$w14chcare3_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare3_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare3_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare3_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare3_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare3_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare3_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare4_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare4_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare4_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare4_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare4_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare4_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare4_1)

GoldbergCallieFiltered_HT$w14chcare4_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare4_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare4_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare4_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare4_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare4_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare4_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare5_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare5_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare5_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare5_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare5_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare5_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare5_1)

GoldbergCallieFiltered_HT$w14chcare5_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare5_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare5_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare5_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare5_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare5_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare5_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare6_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare6_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare6_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare6_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare6_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare6_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare6_1)

GoldbergCallieFiltered_HT$w14chcare6_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare6_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare6_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare6_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare6_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare6_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare6_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare7_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare7_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare7_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare7_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare7_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare7_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare7_1)

GoldbergCallieFiltered_HT$w14chcare7_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare7_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare7_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare7_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare7_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare7_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare7_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare8_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare8_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare8_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare8_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare8_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare8_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare8_1)

GoldbergCallieFiltered_HT$w14chcare8_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare8_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare8_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare8_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare8_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare8_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare8_2)

```



```{r} 
  GoldbergCallieFiltered_HT$w14chcare9_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare9_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare9_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare9_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare9_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare9_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare9_1)

GoldbergCallieFiltered_HT$w14chcare9_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare9_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare9_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare9_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare9_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare9_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare9_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare10_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare10_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare10_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare10_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare10_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare10_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare10_1)

GoldbergCallieFiltered_HT$w14chcare10_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare10_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare10_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare10_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare10_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare10_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare10_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare11_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare11_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare11_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare11_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare11_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare11_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare11_1)

GoldbergCallieFiltered_HT$w14chcare11_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare11_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare11_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare11_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare11_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare11_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare11_2)

```
```{r} 
  GoldbergCallieFiltered_HT$w14chcare12_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare12_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare12_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare12_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare12_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare12_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare12_1)

GoldbergCallieFiltered_HT$w14chcare12_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare12_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare12_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare12_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare12_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare12_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare12_2)

```

```{r} 
  GoldbergCallieFiltered_HT$w14chcare13_1 <- 
  ifelse(GoldbergCallieFiltered$w14chcare13_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare13_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare13_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare13_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare1_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare10_1)

GoldbergCallieFiltered_HT$w14chcare10_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare10_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare10_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare10_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare10_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare10_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare10_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14chcare11_1 <- 
ifelse(GoldbergCallieFiltered$w14chcare11_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare11_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare11_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare11_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare11_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare11_1)

GoldbergCallieFiltered_HT$w14chcare11_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare11_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare11_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare11_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare11_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare11_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare11_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14chcare12_1 <- 
ifelse(GoldbergCallieFiltered$w14chcare12_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare12_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare12_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare12_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare12_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare12_1)

GoldbergCallieFiltered_HT$w14chcare12_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare12_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare12_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare12_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare12_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare12_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare12_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14chcare13_1 <- 
ifelse(GoldbergCallieFiltered$w14chcare13_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare13_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare13_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare13_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare13_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare13_1)

GoldbergCallieFiltered_HT$w14chcare13_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare13_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare13_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare13_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare13_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare13_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare13_2)

```


```{r} 
GoldbergCallieFiltered_HT$w14chcare14_1 <- 
ifelse(GoldbergCallieFiltered$w14chcare14_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare14_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare14_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare14_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare14_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare14_1)

GoldbergCallieFiltered_HT$w14chcare14_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare14_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare14_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare14_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare14_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare14_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare14_2)

```


```{r} 
GoldbergCallieFiltered_HT$w14chcare15_1 <- 
ifelse(GoldbergCallieFiltered$w14chcare15_1==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare15_1==2,2,
ifelse(GoldbergCallieFiltered$w14chcare15_1==3,3,
ifelse(GoldbergCallieFiltered$w14chcare15_1==4,4,
ifelse(GoldbergCallieFiltered$w14chcare15_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14chcare15_1)

GoldbergCallieFiltered_HT$w14chcare15_2 <- 
ifelse(GoldbergCallieFiltered$w14chcare15_2==1, 1,
ifelse(GoldbergCallieFiltered$w14chcare15_2==2,2,
ifelse(GoldbergCallieFiltered$w14chcare15_2==3,3,
ifelse(GoldbergCallieFiltered$w14chcare15_2==4,4,
ifelse(GoldbergCallieFiltered$w14chcare15_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14chcare15_2)

```