---
title: "Restructing data"
author: "Margaret"
date: "October 23, 2019"
output: pdf_document
---

```{r}
#install.packages("psych")
#install.packages("plyr")
library(psysds364data)
library(psych)
library(devtools)
library(tidyr)
library(mosaic)
library(dplyr)
library(ggplot2)
library(plyr)
```


```{r}
#Call data
data("Goldberg_callie")

##sample code referance
attributes(Goldberg_callie$w16activ4_2)
names(select(Goldberg_callie, contains("sex")))
?Goldberg
attributes(Goldberg_callie$w16ra)
cortest<-corr.test(select(Goldberg_callie, w16activ1_2, w16activ2_2, w16activ3_2,w16activ4_2, w16activ5_2, w16activ6_2, w16activ7_2, w16activ8_2,w16activ9_2, w16activ10_2, w16activ11_2))$r
names(select(Goldberg_callie, contains("gender")))

attributes(Goldberg_callie$w16activ10_2)
attributes(Goldberg_callie$w16activ3_2)

```


```{r}
 # ggplot(Goldberg_callie, aes(x=sexor))+
 # #   geom_bar()+
 #  labs(main="Number of Lesbian, Gay, and Heterosexual Couples")

  #scale_x_discrete(limits=c("Same-Sex","Heterosexual"))+

barplot(Goldberg_callie, main="Number of Lesbian, Gay, and Heterosexual Couples", xlab= "Sexual Orientation",ylab="Number of Couples")


```


# Suggested Variable Select
```{r}
dataSelect<- Goldberg_callie%>%
  select(famid, sexor, gender_1, gender_2,  contains("gender"), contains("w16toys"), contains("14hht"), contains("14chcare"),w14CBCLrace_1,w14CBCLrace_2,  contains("w12Gay"), contains("edu"), w11FamInc_1,  contains("activ16"), contains("LGBTCI"), contains("w14CBCLrace_1"),contains("16HHT"),contains("16activ"))


```


```{r}
GoldbergCallieFiltered<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys2_1), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), !is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) , !is.na(w16toys5_2), !is.na(w14HHT1_1), !is.na(w14HHT2_1) , !is.na(w14HHT3_1), !is.na(w14HHT4_2),!is.na(w14HHT5_1),!is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1), !is.na(w14HHT9_1), !is.na(w14HHT10_1), !is.na(w14HHT11_1), !is.na(w14HHT12_1),!is.na(w14HHT13_1),!is.na(w14HHT1_2), !is.na(w14HHT3_2), !is.na(w14HHT4_2), !is.na(w14HHT5_2),!is.na(w14HHT6_2),!is.na(w14HHT7_2), !is.na(w14HHT8_2), !is.na(w14HHT9_2), !is.na(w14HHT10_2), !is.na(w14HHT11_2), !is.na(w14HHT12_2), !is.na(w14HHT13_2),
         !is.na(w16HHT1_1), !is.na(w16HHT2_1) , !is.na(w16HHT3_1), !is.na(w16HHT4_2),!is.na(w16HHT5_1),!is.na(w16HHT6_1), !is.na(w16HHT7_1), !is.na(w16HHT8_1), !is.na(w16HHT9_1), !is.na(w16HHT10_1), !is.na(w16HHT11_1), !is.na(w16HHT12_1),!is.na(w16HHT13_1),!is.na(w16HHT1_2), !is.na(w16HHT3_2), !is.na(w16HHT4_2), !is.na(w16HHT5_2),!is.na(w16HHT6_2),!is.na(w16HHT7_2), !is.na(w16HHT8_2), !is.na(w16HHT9_2), !is.na(w16HHT10_2), !is.na(w16HHT11_2), !is.na(w16HHT12_2), !is.na(w16HHT13_2), !is.na(w16activ1_1),!is.na(w16activ2_1),!is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1))

summary(Goldberg_callie)
```



#Get Demagraphics for 

```{r}
##Demographic data attributes (gender, sexual orentation, regilion)
attributes(Goldberg_callie$gender_1)
attributes(Goldberg_callie$w14CBCLgender_1)
attributes(Goldberg_callie$w14chgender_2)

attributes(Goldberg_callie$w14Religion_1)

attributes(Goldberg_callie$sexor)
attributes(Goldberg_callie$w14AdSex_1)
attributes(Goldberg_callie$w14AdSex_2)

##The occurances of demographic varibles
head(Goldberg_callie)
count(Goldberg_callie, vars= "w14Religion_1")
count(Goldberg_callie, vars= "w14Religion_2")
count(Goldberg_callie, vars= "sexor")
count(Goldberg_callie, vars= "gender_1")
count(Goldberg_callie, vars= "gender_2")
count(Goldberg_callie, vars= "w14AdSex_1")
count(Goldberg_callie, vars = "w14AdSex_2")
count(Goldberg_callie, vars= "w14CBCLgender_1") 
### same freq as w14CBCLgender_2 and quest: there is no documentation for what 3,5, and 22 mean

#sexor based datasets
samesex_gb<- Goldberg_callie%>%
  filter(sexor == 1)

hetero_gb<- Goldberg_callie%>%
  filter(sexor == -1)


```





```{r}
# Demagraphics on 'child's Race
attributes(GoldbergCallieFiltered$w14CBCLrace_1)

count(GoldbergCallieFiltered, var="w14CBCLrace_1")

```


```{r}
ggplot(Goldberg_callie, aes(x=w14CBCLrace_1))+
  geom_histogram()


```


In our data set we have 
```{r}

#  Demagraphics on Family Income
attributes(GoldbergCallieFiltered$w11FamInc_1)
summary(GoldbergCallieFiltered$w11FamInc_1 )

```

The study had a wide range of family income distribution. With a median of $118,250 earned by a family per year.

```{r}
ggplot(Goldberg_callie, aes(x=w11FamInc_1))+
  geom_histogram()+
  labs(y="Number of Families", x="Household Income")


```




```{r}

#Eucation
attributes(GoldbergCallieFiltered$w11Educ_1)
attributes(GoldbergCallieFiltered$w11Educ_2)

count(GoldbergCallieFiltered, var="w11Educ_1")
count(GoldbergCallieFiltered, var="w11Educ_2")


```
For distribution of eduction it was found that 44 particpants had less than high school for education, 30 had a high school diploma or higher.

```{r}
CollegePlus_1<- GoldbergCallieFiltered%>%
  filter(w11Educ_1!=1,w11Educ_1!=2)

CollegePlus_2<- GoldbergCallieFiltered%>%
  filter(w11Educ_2!=1,w11Educ_2!=2)

```


```{r}
count(Goldberg_callie,var="CollegePlus_1" )
count(Goldberg_callie,var="CollegePlus_2" )

```

* Coincidental?

```{r}


```


```{r}
# Race
attributes(GoldbergCallieFiltered$w11Race_2)
attributes(GoldbergCallieFiltered$w14CBCLrace_1)

count(Goldberg_callie, var="w11Race_2")
count(Goldberg_callie, var="w14CBCLrace_1")


# Income
attributes(Goldberg_callie$w11FamInc_1)
summary(GoldbergCallieFiltered$w11FamInc_1 )

#Eucation
attributes(GoldbergCallieFiltered$w11Educ_1)
attributes(GoldbergCallieFiltered$w11Educ_2)

count(GoldbergCallieFiltered, var="w11Educ_1")
count(GoldbergCallieFiltered, var="w11Educ_2")

```

```{r}          
Goldberg_callie2<- Goldberg_callie%>%
  mutate(ww11FamInc=as.integer(w11FamInc_1))%>%
mutate( w11FamInc= ifelse(w11FamInc_1 %in% 0:20000, "20k or less", ifelse(w11FamInc_1 %in% 20001:40000, "20k-40k", ifelse(w11FamInc_1 %in% 40001:60000, "40k-60k", ifelse(w11FamInc_1 %in% 60001:80000, "60k-80k", ifelse(w11FamInc_1 %in% 80001:100000, "80k-100k", ifelse(w11FamInc_1 %in% 100001:730000, "10000k+", "NA" )))))))

Goldberg_callieViewable2<- Goldberg_callie2%>%
  select(w11FamInc)
View(Goldberg_callie2)



```


For the study, our sample size includes 
```{r}
attributes(Goldberg_callie2$w11FamInc)
attributes(Goldberg_callie$w11FamInc_1)
count(Goldberg_callie2, var="w11FamInc")
count(Goldberg_callie, var="w11FamInc_1")
#ggplot(Goldberg_callie2, aes(x= w11FamInc))+geom_histogram()

summary(Goldberg_callie2$w11FamInc)

```




```{r}
FamIncome<- GoldbergCallieFiltered%>%
  filter(w11FamInc)
count(Goldberg_callie2, var="w11FamInc")


```


```{r}
Test<- Goldberg_callie%>%
  filter(w11FamInc==)


```















The study included data from 223 families that made $100,000 or more while 







