---
title             : "PSY/SDS 364: Resutls Write Up"
shorttitle        : "Measures and Descriptive Statistic"

author: 
  - name          : "Margret Perry"
    affiliation   : "1"
  - name          : "Callie Selvin"
    affliation    : "2"
  - name          : "Isabel Zamudio-Moore"
    affliation    : "3"
  
    corresponding : yes    # Define only one corresponding author
    address       : "Northampton, MA"
    email         : "izamudiomoore@smith.edu"

affiliation:
  - id            : "1"
    institution   : "Smith College"

author_note: >
  Smith College
  
keywords          : "Division of Labor, Gender Role Development, Preschool Activities Inventory"
wordcount         : "X"

bibliography      : ["MDSreferences.bib","r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library(papaja)
library(mosaic)
library(psych)
```

```{r create_r-references}
r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "MDSreferences.bib")
```


```{r}
#install.packages("psych")
#install.packages("plyr")
library(psysds364data)
library(devtools)
library(tidyr)
library(mosaic)
library(dplyr)
library(ggplot2)
library(plyr)
```

# Dataset: Goldberg

# Question: How does the display of gender roles in children vary with the change in delegation of household responsibilities between parents?

#Analysis Strategy Section+Hypothesis

#Remind reaader of resrach question
Our resaerch seeks to look out the question of how the display of gender roles in children vary with the change in delegation of household responsibilities between parents?


2. Dyadic Data Analaysis
3. Take a figure of this.
4. Talk about data processing and how we
arrived at the model.


```{r}
#Call data
data("Goldberg_callie")

##sample code referance
attributes(Goldberg_callie$w16activ4_2)
names(select(Goldberg_callie, contains("sex")))
?Goldberg
attributes(Goldberg_callie$w16ra)
cortest<-corr.test(select(Goldberg_callie, w16activ1_2, w16activ2_2, w16activ3_2,w16activ4_2, w16activ5_2, w16activ6_2, w16activ7_2, w16activ8_2,w16activ9_2, w16activ10_2, w16activ11_2))$r
names(select(Goldberg_callie, contains("gender")))

attributes(Goldberg_callie$w16activ10_2)
attributes(Goldberg_callie$w16activ3_2)

```




```{r include = FALSE}
GoldbergCallieFiltered<- Goldberg_callie%>% 
  filter(!is.na(famid), !is.na(gender_1), !is.na(sexor), !is.na(gender_2),  !is.na(w16toys1_1), !is.na(w16toys1_2), !is.na(w16toys3_1), !is.na(w16toys4_1), !is.na(w16toys5_1), !is.na(w16toys6_1), !is.na(w16toys7_1), 
!is.na(w16toys2_1), !is.na(w16toys2_2), !is.na(w16toys3_2), !is.na(w16toys4_2), !is.na(w16toys5_2), !is.na(w16toys6_2), !is.na(w16toys7_2) ,
!is.na(w14HHT1_1), !is.na(w14HHT2_1) , !is.na(w14HHT3_1), !is.na(w14HHT4_1), !is.na(w14HHT5_1), !is.na(w14HHT6_1), !is.na(w14HHT7_1), !is.na(w14HHT8_1), !is.na(w14HHT9_1), !is.na(w14HHT10_1), !is.na(w14HHT11_1), !is.na(w14HHT12_1), !is.na(w14HHT13_1),
!is.na(w14HHT1_2), !is.na(w14HHT2_2), !is.na(w14HHT3_2), !is.na(w14HHT4_2), !is.na(w14HHT5_2),!is.na(w14HHT6_2), !is.na(w14HHT7_2), !is.na(w14HHT8_2), !is.na(w14HHT9_2), !is.na(w14HHT10_2), !is.na(w14HHT11_2), !is.na(w14HHT12_2), !is.na(w14HHT13_2), 
!is.na(w16activ1_1), !is.na(w16activ2_1), !is.na(w16activ3_1), !is.na(w16activ4_1), !is.na(w16activ5_1), !is.na(w16activ6_1), !is.na(w16activ7_1), !is.na(w16activ8_1), !is.na(w16activ9_1), !is.na(w16activ10_1), !is.na(w16activ11_1),
!is.na(w16activ1_2), !is.na(w16activ2_2), !is.na(w16activ3_2), !is.na(w16activ4_2), !is.na(w16activ5_2), !is.na(w16activ6_2), !is.na(w16activ7_2), !is.na(w16activ8_2), !is.na(w16activ9_2), !is.na(w16activ10_2),
!is.na(w16activ11_2),
!is.na(w16charac1_1), !is.na(w16charac2_1), !is.na(w16charac3_1), !is.na(w16charac4_1), !is.na(w16charac5_1), !is.na(w16charac6_1), 

!is.na(w16charac1_2), !is.na(w16charac2_2), !is.na(w16charac3_2), !is.na(w16charac4_2), !is.na(w16charac5_2), !is.na(w16charac6_2)
   )


```

```{r}
summary(GoldbergCallieFiltered$w14HHT2_1)


```


```{r}
GoldbergCallieFiltered_HT<- GoldbergCallieFiltered

summary(GoldbergCallieFiltered_HT$w14HHT2_1 )

GoldbergCallieFiltered_HT$w14HHT1_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT1_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT1_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT1_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT1_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT1_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14HHT1_2)

  GoldbergCallieFiltered_HT$w14HHT1_2 <- 
  ifelse(GoldbergCallieFiltered$w14HHT1_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT1_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT1_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT1_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT1_2==5,5, 88)))))


summary(GoldbergCallieFiltered_HT$w14HHT1_1)

```
```{r} 
  GoldbergCallieFiltered_HT$w14HHT2_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT2_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT2_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT2_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT2_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT2_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT2_1)

  GoldbergCallieFiltered_HT$w14HHT2_2 <- 
  ifelse(GoldbergCallieFiltered$w14HHT2_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT2_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT2_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT2_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT2_2==5,5, 88)))))
  
  summary(GoldbergCallieFiltered_HT$w14HHT2_2)


```




```{r} 
  GoldbergCallieFiltered_HT$w14HHT3_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT3_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT3_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT3_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT3_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT3_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT3_1)

  GoldbergCallieFiltered_HT$w14HHT3_2 <- 
  ifelse(GoldbergCallieFiltered$w14HHT3_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT3_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT3_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT3_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT3_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT3_2)


```



```{r} 
  GoldbergCallieFiltered_HT$w14HHT4_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT4_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT4_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT4_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT4_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT4_1==5,5, 88)))))
summary(GoldbergCallieFiltered_HT$w14HHT4_1)

GoldbergCallieFiltered_HT$w14HHT4_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT4_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT4_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT4_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT4_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT4_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT4_2)


```

```{r} 
GoldbergCallieFiltered_HT$w14HHT5_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT5_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT5_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT5_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT5_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT5_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT5_1)

GoldbergCallieFiltered_HT$w14HHT5_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT5_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT5_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT5_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT5_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT5_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT5_2)

```
```{r} 
  GoldbergCallieFiltered_HT$w14HHT6_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT6_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT6_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT6_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT6_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT6_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT6_1)
GoldbergCallieFiltered_HT$w14HHT6_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT6_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT6_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT6_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT6_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT6_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT6_2)


```

```{r} 
  GoldbergCallieFiltered_HT$w14HHT7_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT7_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT7_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT7_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT7_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT7_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT7_1)

  GoldbergCallieFiltered_HT$w14HHT7_2 <- 
  ifelse(GoldbergCallieFiltered$w14HHT7_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT7_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT7_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT7_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT7_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT7_2)


```

```{r} 
  GoldbergCallieFiltered_HT$w14HHT9_1 <- 
  ifelse(GoldbergCallieFiltered$w14HHT9_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT9_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT9_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT9_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT9_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT9_1)

  GoldbergCallieFiltered_HT$w14HHT9_2 <- 
  ifelse(GoldbergCallieFiltered$w14HHT9_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT9_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT9_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT9_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT9_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT9_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14HHT10_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT10_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT10_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT10_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT10_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT10_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT10_1)

GoldbergCallieFiltered_HT$w14HHT10_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT10_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT10_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT10_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT10_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT10_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT10_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14HHT11_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT11_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT11_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT11_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT11_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT11_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT11_1)

GoldbergCallieFiltered_HT$w14HHT11_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT11_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT11_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT11_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT11_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT11_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT11_2)

```
```{r} 
GoldbergCallieFiltered_HT$w14HHT12_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT12_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT12_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT12_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT12_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT12_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT12_1)

GoldbergCallieFiltered_HT$w14HHT12_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT12_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT12_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT12_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT12_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT12_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT12_2)

```

```{r} 
GoldbergCallieFiltered_HT$w14HHT13_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT13_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT13_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT13_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT13_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT13_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT13_1)

GoldbergCallieFiltered_HT$w14HHT13_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT13_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT13_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT13_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT13_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT13_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT13_2)

```


```{r} 
GoldbergCallieFiltered_HT$w14HHT14_1 <- 
ifelse(GoldbergCallieFiltered$w14HHT14_1==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT14_1==2,2,
ifelse(GoldbergCallieFiltered$w14HHT14_1==3,3,
ifelse(GoldbergCallieFiltered$w14HHT14_1==4,4,
ifelse(GoldbergCallieFiltered$w14HHT14_1==5,5, 88)))))

summary(GoldbergCallieFiltered_HT$w14HHT14_1)

GoldbergCallieFiltered_HT$w14HHT14_2 <- 
ifelse(GoldbergCallieFiltered$w14HHT14_2==1, 1,
ifelse(GoldbergCallieFiltered$w14HHT14_2==2,2,
ifelse(GoldbergCallieFiltered$w14HHT14_2==3,3,
ifelse(GoldbergCallieFiltered$w14HHT14_2==4,4,
ifelse(GoldbergCallieFiltered$w14HHT14_2==5,5, 88)))))
  
summary(GoldbergCallieFiltered_HT$w14HHT14_2)

```

```{r}
#Get the mean of all tasks
MEAN_ALL_2<-
  mean(GoldbergCallieFiltered_HT$w14HHT1_2+
      GoldbergCallieFiltered_HT$w14HHT2_2+
      GoldbergCallieFiltered_HT$w14HHT3_2+
      GoldbergCallieFiltered_HT$w14HHT4_2+
      GoldbergCallieFiltered_HT$w14HHT5_2+
      GoldbergCallieFiltered_HT$w14HHT6_2+
      GoldbergCallieFiltered_HT$w14HHT7_2+
      GoldbergCallieFiltered_HT$w14HHT8_2+
      GoldbergCallieFiltered_HT$w14HHT9_2+
      GoldbergCallieFiltered_HT$w14HHT10_2+
      GoldbergCallieFiltered_HT$w14HHT11_2+
      GoldbergCallieFiltered_HT$w14HHT12_2+
      GoldbergCallieFiltered_HT$w14HHT13_2+
      GoldbergCallieFiltered_HT$w14HHT14_2)
#
MEAN_ALL_2
```

```{r}
#Get the mean of all tasks
MEAN_ALL_1<-
  mean(GoldbergCallieFiltered_HT$w14HHT1_1+
      GoldbergCallieFiltered_HT$w14HHT2_1+
      GoldbergCallieFiltered_HT$w14HHT3_1+
      GoldbergCallieFiltered_HT$w14HHT4_1+
      GoldbergCallieFiltered_HT$w14HHT5_1+
      GoldbergCallieFiltered_HT$w14HHT6_1+
      GoldbergCallieFiltered_HT$w14HHT7_1+
      GoldbergCallieFiltered_HT$w14HHT8_1+
      GoldbergCallieFiltered_HT$w14HHT9_1+
      GoldbergCallieFiltered_HT$w14HHT10_1+
      GoldbergCallieFiltered_HT$w14HHT11_1+
      GoldbergCallieFiltered_HT$w14HHT12_1+
      GoldbergCallieFiltered_HT$w14HHT13_1+
      GoldbergCallieFiltered_HT$w14HHT14_1)
#
MEAN_ALL_1
```

```{r}
#Get the mean of all tasks
MEAN_F_1<-
  mean(GoldbergCallieFiltered_HT$w14HHT1_1+
      GoldbergCallieFiltered_HT$w14HHT2_1+
      GoldbergCallieFiltered_HT$w14HHT3_1+
      GoldbergCallieFiltered_HT$w14HHT4_1+
        #7 not masculine nor feminine
    GoldbergCallieFiltered_HT$w14HHT8_1+
      GoldbergCallieFiltered_HT$w14HHT9_1+
        #12 not masculine nor feminine
    GoldbergCallieFiltered_HT$w14HHT13_1+
      GoldbergCallieFiltered_HT$w14HHT14_1)
#
MEAN_M_1<-
  mean(GoldbergCallieFiltered_HT$w14HHT5_1+
      GoldbergCallieFiltered_HT$w14HHT6_1+
      GoldbergCallieFiltered_HT$w14HHT10_1+
      GoldbergCallieFiltered_HT$w14HHT11_1)

MEAN_F_1
MEAN_M_1
```

```{r}
#Get the mean of all tasks
MEAN_F_2<-
  mean(GoldbergCallieFiltered_HT$w14HHT1_2+
      GoldbergCallieFiltered_HT$w14HHT2_2+
      GoldbergCallieFiltered_HT$w14HHT3_2+
      GoldbergCallieFiltered_HT$w14HHT4_2+
        #7 not masculine nor feminine
    GoldbergCallieFiltered_HT$w14HHT8_2+
      GoldbergCallieFiltered_HT$w14HHT9_2+
        #12 not masculine nor feminine
    GoldbergCallieFiltered_HT$w14HHT13_2+
      GoldbergCallieFiltered_HT$w14HHT14_2)
#
MEAN_M_2<-
  mean(GoldbergCallieFiltered_HT$w14HHT5_2+
      GoldbergCallieFiltered_HT$w14HHT6_2+
      GoldbergCallieFiltered_HT$w14HHT10_2+
      GoldbergCallieFiltered_HT$w14HHT11_2)

MEAN_F_2
MEAN_M_2
```


```{r}
#Get the mean of all tasks


```
#Main Result Section
1. Write about coeficents.
2. Figure
3. EDA

*pvalue,SE use three decimal points
*coef use two decimal points

round(coef,#decminal)



