---
title             : "PSY/SDS 364: Research Project Results Write Up"
shorttitle        : "Results Write Up"

author: 
  - name          : "Margret Perry"
    affiliation   : "1"
  - name          : "Callie Slevin"
    affliation    : "2"
  - name          : "Isabel Zamudio-Moore"
    affliation    : "3"
  
    corresponding : yes    # Define only one corresponding author
    address       : "Northampton, MA"
    email         : "izamudiomoore@smith.edu"

affiliation:
  - id            : "1"
    institution   : "Smith College"

author_note: >
  Smith College
  
keywords          : "Division of Labor, Gender Role Development, Preschool Activities Inventory"
wordcount         : "X"

bibliography      : ["MDSreferences.bib","r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
#library(papaja)
library(mosaic)
library(psych)
#install.packages("psych")
#install.packages("plyr")
#library(psysds364data)
library(devtools)
library(tidyr)
library(dplyr)
library(ggplot2)
library(plyr)
library(nlme)
```

#Analysis Strategy


```{r create_r-references, include = FALSE}
r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "MDSreferences.bib")
```
# Dataset: Goldberg


# Question:We hypothesized that the division of household labor medigates the affect of sexual orientation on gender display in preschool aged childern.


#Analysis Strategy Section+Hypothesis

#Remind reader of research question
Our research seeks to look out the question of how the display of gender roles in children vary with the change in delegation of household responsibilities between parents?


 

2. Dyadic Data Analaysis
3. Take a figure of this.
4. Talk about data processing and how we
arrived at the model.

Data Processing

#Scale Score



```{rinclude=FALSE}


data("Goldberg_callie")
Goldberg_Callie_2<- Goldberg_callie

```

```{r include=FALSE}

#Scale Score
Goldberg_Callie_SR<- Goldberg_Callie_2%>%
mutate(SR_PSAc1_1=0, SR_PSAc2_1=0, SR_PSAc3_1=0, SR_PSAc4_1=0, SR_PSAc5_1=0, SR_PSAc6_1=0,
SR_PSAa1_1=0, SR_PSAa2_1=0, SR_PSAa3_1=0, SR_PSAa4_1=0, SR_PSAa5_1=0, SR_PSAa6_1=0, SR_PSAa7_1=0, SR_PSAa8_1=0, SR_SR_PSAa9_1=0, SR_PSAa10_1=0, SR_PSAa11_1=0,
SR_PSAt1_1=0, SR_PSAt2_1=0, SR_PSAt3_1=0, SR_PSAt4_1=0, SR_PSAt5_1=0, SR_PSAt6_1=0, SR_PSAt7_1=0)

#Create binary variables for wether a specific variable has been recorded for Person 1
#Binary for character
Goldberg_Callie_SR$SR_PSAc1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac1_1), 1,0)

Goldberg_Callie_SR$SR_PSAc2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac2_1),1,0)

Goldberg_Callie_SR$SR_PSAc3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac3_1),1,0)

Goldberg_Callie_SR$SR_PSAc4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac4_1),1,0)

Goldberg_Callie_SR$SR_PSAc5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac5_1),1,0)

Goldberg_Callie_SR$SR_PSAc6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac6_1),1,0)

#Binary for activity
Goldberg_Callie_SR$SR_PSAa1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ1_1),1,0)

Goldberg_Callie_SR$SR_PSAa2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ2_1),1,0)

Goldberg_Callie_SR$SR_PSAa3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ3_1),1,0)

Goldberg_Callie_SR$SR_PSAa4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ4_1),1,0)

Goldberg_Callie_SR$SR_PSAa5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ5_1),1,0)


Goldberg_Callie_SR$SR_PSAa6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ6_1),1,0)

Goldberg_Callie_SR$SR_PSAa7_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ7_1),1,0)


Goldberg_Callie_SR$SR_PSAa8_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ8_1),1,0)


Goldberg_Callie_SR$SR_PSAa9_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ9_1),1,0)


Goldberg_Callie_SR$SR_PSAa10_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ10_1),1,0)

Goldberg_Callie_SR$SR_PSAa11_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ11_1),1,0)

Goldberg_Callie_SR$SR_PSAt1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys1_1),1,0)

Goldberg_Callie_SR$SR_PSAt2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys2_1),1,0)

Goldberg_Callie_SR$SR_PSAt3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys3_1),1,0)

Goldberg_Callie_SR$SR_PSAt4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys4_1),1,0)

Goldberg_Callie_SR$SR_PSAt5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys5_1),1,0)

Goldberg_Callie_SR$SR_PSAt6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys6_1),1,0)

Goldberg_Callie_SR$SR_PSAt7_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys7_1),1,0)

#SR_PSAc3=w16charac3_1,     SR_PSAc4= w16charac4_1, SR_PSAc1=w16charac5_1,     SR_PSAc6= w16charac6_1, 
 # SR_PSAc1=w16charac1_1)
#summary(Goldberg_Callie_SR$SR_PSAc1)
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI_1=SR_PSAc1_1+ SR_PSAc2_1+ SR_PSAc3_1+ SR_PSAc4_1+ SR_PSAc5_1+ SR_PSAc6_1+
SR_PSAa1_1+ SR_PSAa2_1+ SR_PSAa3_1+ SR_PSAa4_1+ SR_PSAa5_1+ SR_PSAa6_1+ SR_PSAa7_1+ SR_PSAa8_1, SR_PSAa9_1+ SR_PSAa10_1, SR_PSAa11_1+
SR_PSAt1_1+ SR_PSAt2_1, SR_PSAt3_1, SR_PSAt4_1, SR_PSAt5_1+ SR_PSAt6_1, SR_PSAt7_1)

```

```{r, include = FALSE}
#Scale Score

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PSAc1_2=0, SR_PSAc2_2=0, SR_PSAc3_2=0, SR_PSAc4_2=0, SR_PSAc5_2=0, SR_PSAc6_2=0,
SR_PSAa1_2=0, SR_PSAa2_2=0, SR_PSAa3_2=0, SR_PSAa4_2=0, SR_PSAa5_2=0, SR_PSAa6_2=0, SR_PSAa7_2=0, SR_PSAa8_2=0, SR_PSAa9_2=0, SR_PSAa10_2=0, SR_PSAa11_2=0,
SR_PSAt2_2=0, SR_PSAt2_2=0, SR_PSAt3_2=0, SR_PSAt4_2=0, SR_PSAt5_2=0, SR_PSAt6_2=0, SR_PSAt7_2=0)

#Create binary variables for wether a specific variable has been recorded for Person 1
#Binary for character
Goldberg_Callie_SR$SR_PSAc1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac1_2), 1,0)

Goldberg_Callie_SR$SR_PSAc2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac2_2),1,0)

Goldberg_Callie_SR$SR_PSAc3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac3_2),1,0)

Goldberg_Callie_SR$SR_PSAc4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac4_2),1,0)

Goldberg_Callie_SR$SR_PSAc5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac5_2),1,0)

Goldberg_Callie_SR$SR_PSAc6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac6_2),1,0)

#Binary for activity
Goldberg_Callie_SR$SR_PSAa1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ1_2),1,0)

Goldberg_Callie_SR$SR_PSAa2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ2_2),1,0)

Goldberg_Callie_SR$SR_PSAa3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ3_2),1,0)

Goldberg_Callie_SR$SR_PSAa4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ4_2),1,0)

Goldberg_Callie_SR$SR_PSAa5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ5_2),1,0)


Goldberg_Callie_SR$SR_PSAa6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ6_2),1,0)

Goldberg_Callie_SR$SR_PSAa7_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ7_2),1,0)


Goldberg_Callie_SR$SR_PSAa8_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ8_2),1,0)


Goldberg_Callie_SR$SR_PSAa9_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ9_2),1,0)


Goldberg_Callie_SR$SR_PSAa10_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ10_2),1,0)

Goldberg_Callie_SR$SR_PSAa11_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ11_2),1,0)

Goldberg_Callie_SR$SR_PSAt1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys1_2),1,0)

Goldberg_Callie_SR$SR_PSAt2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys2_2),1,0)

Goldberg_Callie_SR$SR_PSAt3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys3_2),1,0)

Goldberg_Callie_SR$SR_PSAt4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys4_2),1,0)

Goldberg_Callie_SR$SR_PSAt5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys5_2),1,0)

Goldberg_Callie_SR$SR_PSAt6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys6_2),1,0)

Goldberg_Callie_SR$SR_PSAt7_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys7_2),1,0)

#SR_PSAc3=w16charac3_1,     SR_PSAc4= w16charac4_1, SR_PSAc1=w16charac5_1,     SR_PSAc6= w16charac6_1, 
 # SR_PSAc1=w16charac1_1)
#summary(Goldberg_Callie_SR$SR_PSAc1)
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI_2=SR_PSAc1_2+ SR_PSAc2_2+ SR_PSAc3_2+ SR_PSAc4_2+ SR_PSAc5_2+ SR_PSAc6_2+
SR_PSAa1_2+ SR_PSAa2_2+ SR_PSAa3_2+ SR_PSAa4_2+ SR_PSAa5_2+ SR_PSAa6_2+ SR_PSAa7_2+ SR_PSAa8_2, SR_PSAa9_2+ SR_PSAa10_2, SR_PSAa11_2+
SR_PSAt1_2+ SR_PSAt2_2, SR_PSAt3_2, SR_PSAt4_2, SR_PSAt5_2+ SR_PSAt6_2, SR_PSAt7_2)

```

```{r, include = FALSE}
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI=SR_PAI_1+SR_PAI_2)

```


```{r, include = FALSE}
ActNum<- 7+6+11
ActNum<- ActNum*2
CoupwOneP<- ActNum*0.01
CoupwTenP<- ActNum*0.05
CoupwFiveP<- ActNum*0.1


```

```{r, include = FALSE}
Original<- nrow(Goldberg_Callie_SR)
```

```{r, include = FALSE}
Goldberg_Callie_SR_10<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwTenP)

NumPartwTen<-nrow(Goldberg_Callie_SR_10)

Goldberg_Callie_SR_5<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwFiveP)

NumPartwFive<-nrow(Goldberg_Callie_SR_5)

Goldberg_Callie_SR_1<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwOneP)

NumPartwOne<-nrow(Goldberg_Callie_SR_1)



```


```{r, include = FALSE}
PartwTenPer<- NumPartwTen/Original
PartwTenPer

PartwFivePer<-  NumPartwFive/Original
PartwFivePer

PartwOnePer<- NumPartwOne/Original
PartwOnePer
```



In our data processing, it was decided that we would work with a scale score and would only exclude participants if the participant answered at least 5% of questions. This would only allow us to keep only a little over half of our paricipants in the study, `r printnum(PartwOnePer)` It was decided that regardless of the scale score partipants would be included in the study.



```{r, include = FALSE}
#Call data
data("Goldberg_callie")

##sample code referance
attributes(Goldberg_callie$w16activ4_2)
names(select(Goldberg_callie, contains("sex")))
?Goldberg
attributes(Goldberg_callie$w16ra)
cortest<-corr.test(select(Goldberg_callie, w16activ1_2, w16activ2_2, w16activ3_2,w16activ4_2, w16activ5_2, w16activ6_2, w16activ7_2, w16activ8_2,w16activ9_2, w16activ10_2, w16activ11_2))$r
names(select(Goldberg_callie, contains("gender")))

attributes(Goldberg_callie$w16activ10_2)
attributes(Goldberg_callie$w16activ3_2)
```


To arrive at the model, we worked to standardize information based on gender and the age of the child working of the standardization models found by Garcia et al.

#Child Gender Data
```{r, include = FALSE}
 summary(Goldberg_Callie_SR$w14chgender_1)
```

```{r, include = FALSE}
names(select(Goldberg_callie, contains("chage")))
```

```{r,include = FALSE}

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(w16chagemo=0)

AgeSubset<- Goldberg_Callie_SR%>%
  select(famid, partnum, w16chagemo_1,w16chagemo_2)

AgeMatrix<- as.matrix(AgeSubset)
AgeMatrixSub<- AgeMatrix[ ,3:4]
AgeMeans<- rowMeans(AgeMatrixSub)
head(AgeMatrixSub)
#View(AgeMeans)
AgeMatrix<-cbind(AgeMatrix, AgeMeans)
AgeMRejoin<-as.data.frame(AgeMatrix)
#View(AgeMatrix)
#View(AgeMRejoin)

Goldberg_Callie_SR<-join(AgeMRejoin,Goldberg_Callie_SR)
#View(Rejoin)

```

```{r, include = FALSE}
 summary(Goldberg_Callie_SR$w14chgender_1)
```

```{r, include = FALSE}
names(select(Goldberg_callie, contains("chage")))
```

```{r, include = FALSE}

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(PAIfin=0)

```






#Models|

<p> 
Hypothesis 1: 
We hypothesized that the division of household labor medigates the affect of sexual orientation on gender display in preschool aged childern.

<p> 
Hypothesis 2: 
We hypothesize that unequal division of labor in heterosexual couples will have a greater effect on gender play in children than the labor disruption in same-sex couples.

<p> 
Hypothesis 3:  
We hypothesize that the division of labor will be associated with having a larger effect on whether a child display displays gender-typed play than the family structure.


Defining our models
```{r, include = FALSE}


```



#Main Result Section
1. Write about coeficents.
2. Figure
3. EDA

*pvalue,SE use three decimal points
*coef use two decimal points

round(coef,#decminal)



```{r, include = FALSE}
 AgeSubset<- Goldberg_Callie_SR%>%
   select(famid, partnum,w16chagemo_1,w16chagemo_2)
# # 
head(AgeSubset)
```



```{r, include = FALSE}
AgeSubsetMatrix<- as.matrix(AgeSubset)
AgeSubsetMatrix<- AgeSubsetMatrix[ ,3:4]
AgeMeans<-colMeans(AgeMatrixSub)
#View(PAISubsetMatrix)
#View(AgeMeans)
AgeMatrix<-cbind(AgeMatrix,AgeMeans)
AgeMRejoin<-as.data.frame(AgeMatrix)
#View(AgeMatrix)
#View(AgeMRejoin)

Goldberg_Callie_SR<-join(AgeMRejoin,Goldberg_Callie_SR)
#View(Rejoin)

```

```{r, include = FALSE}


goldberg_psai<- Goldberg_callie %>%
  select(w16activ1_1, w16activ2_1, w16activ3_1,w16activ4_1, w16activ5_1, w16activ6_1, w16activ7_1, w16activ8_1,w16activ9_1, w16activ10_1, w16activ11_1, w16toys1_1, w16toys2_1, w16toys3_1, w16toys4_1, w16toys5_1, w16toys6_1, w16toys7_1, w16charac1_1, w16charac2_1, w16charac3_1, w16charac4_1, w16charac5_1, w16charac6_1) %>%
  
  mutate(w16rt2= 6- w16toys2_1,w16rt4 = 6- w16toys4_1, w16rt7 = 6- w16toys7_1,w16ra1 = 6- w16activ1_1, w16ra2 = 6- w16activ2_1, w16ra3 = 6- w16activ3_1, w16ra6 = 6- w16activ6_1, w16ra9 = 6- w16activ9_1, w16ra11 = 6- w16activ11_1,w16rc4 = 6- w16charac4_1,w16rc5 = 6- w16charac5_1,w16rc6 = 6- w16charac6_1)

psai_alpha <- goldberg_psai %>%
  select(w16rt2, w16rt4, w16rt7, w16ra1, w16ra2, w16ra3, w16ra6, w16ra9, w16ra11, w16rc4, w16rc5, w16rc6, w16charac1_1, w16charac2_1, w16charac3_1, w16toys1_1, w16toys3_1, w16toys5_1, w16toys6_1, w16activ4_1, w16activ5_1, w16activ7_1, w16activ8_1, w16activ10_1)

psai_alpha_0 <- psai_alpha %>%
  mutate(pai= round((w16rt2+ w16rt4+ w16rt7 + w16ra1 + w16ra2 + w16ra3 + w16ra6 + w16ra9 + w16ra11 + w16rc4 + w16rc5 + w16rc6 + w16charac1_1+ w16charac2_1+ w16charac3_1+ w16toys1_1+ w16toys3_1 + w16toys5_1+ w16toys6_1+ w16activ4_1+ w16activ5_1+ w16activ7_1+ w16activ8_1+ w16activ10_1) /23))



Goldberg_callie$w16PSAI <- rowMeans(goldberg_psai %>% select(w16rt2, w16rt4, w16rt7, w16ra1, w16ra2, w16ra3, w16ra6, w16ra9, w16ra11, w16rc4, w16rc5, w16rc6, w16charac1_1, w16charac2_1, w16charac3_1, w16toys1_1, w16toys3_1, w16toys5_1, w16toys6_1, w16activ4_1, w16activ5_1, w16activ7_1, w16activ8_1, w16activ10_1), na.rm = TRUE)

#cronbach(psai_alpha)


goldberg_hw<- Goldberg_callie%>%
  select(w14HHT1_1:w14HHT13_1)
hw<- corr.test(goldberg_hw)$r
hw
hw_a<- alpha(hw)
#cronbach(goldberg_hw)
```

```{r, include = FALSE}

#PSAI Final score

Goldberg_Callie_SR$w16PSAI_1 <- rowMeans(goldberg_psai %>% select(w16rt2, w16rt4, w16rt7, w16ra1, w16ra2, w16ra3, w16ra6, w16ra9, w16ra11, w16rc4, w16rc5, w16rc6, w16charac1_1, w16charac2_1, w16charac3_1, w16toys1_1, w16toys3_1, w16toys5_1, w16toys6_1, w16activ4_1, w16activ5_1, w16activ7_1, w16activ8_1, w16activ10_1), na.rm = TRUE)

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(w16rt2_2= 6- w16toys2_2, w16rt4_2 = 6- w16toys4_2, w16rt7_2 = 6- w16toys7_2, w16ra1_2 = 6- w16activ1_2, w16ra2_2 = 6- w16activ2_2, w16ra3_2= 6- w16activ3_2, w16ra6_2 = 6- w16activ6_2, w16ra9_2 = 6- w16activ9_2, w16ra11_2= 6- w16activ11_2, w16rc4_2 = 6- w16charac4_2, w16rc5_2 = 6- w16charac5_2, w16rc6_2 = 6- w16charac6_2)


Goldberg_Callie_SR$w16PSAI_2 <- rowMeans(select(Goldberg_Callie_SR, w16rt2_2, w16rt4_2, w16rt7_2, w16ra1_2, w16ra2_2, w16ra3_2, w16ra6_2, w16ra9_2, w16ra11_2, w16rc4_2, w16rc5_2, w16rc6_2, w16charac1_2, w16charac2_2, w16charac3_2, w16toys1_2, w16toys3_2, w16toys5_2, w16toys6_2, w16activ4_2, w16activ5_2, w16activ7_2, w16activ8_2, w16activ10_2), na.rm = TRUE)

```


```{r}
Goldberg_Callie_SR %>%
  group_by(w14chgender_1) %>%
  summarise(mean = mean(w16PSAI_1, na.rm = TRUE))

library(mosaic) 
favstats(w16PSAI_1 ~ w14chgender_1, data = Goldberg_Callie_SR)
```


```{r, include = FALSE}

# Goldberg_Callie_SR<-Goldberg_Callie_SR%>%
#   mutate(w16PSAI_1 = ifelse(Goldberg_Callie_SR$w14chgender_1==-1,
#             Goldberg_Callie_SR$w16PSAI*1.075-Goldberg_Callie_SR$AgeMeans*0.177+0.088 ,
#  ifelse(Goldberg_Callie_SR$w14chgender_1==1,
#            Goldberg_Callie_SR$w16PSAI*1.026-Goldberg_Callie_SR$AgeMeans*0.218+8.33, "NA")))

Goldberg_Callie_SR<-Goldberg_Callie_SR%>%
  mutate(w16PSAI = as.numeric(w16PSAI))

```


```{r, include = FALSE}
Goldberg_Callie_SR<-Goldberg_callie%>%
  mutate(HHT_HouseMean_1= rowMeans(select(Goldberg_callie, w14HHT1_1:w14HHT14_1), na.rm= TRUE))%>%
  mutate(HHT_HouseMean_2= rowMeans(select(Goldberg_callie, w14HHT1_2, w14HHT2_2, w14HHT3_2, w14HHT4_2, w14HHT5_2, w14HHT6_2,w14HHT7_2, w14HHT8_2, w14HHT9_2, w14HHT10_2, w14HHT11_2, w14HHT12_2, w14HHT13_2, w14HHT14_2), na.rm = TRUE))
                                   
          


```


```{r, include = FALSE}
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(EqualPercp= ifelse(HHT_HouseMean==3, 1, 0))

```




```{r}

count(Goldberg_Callie_SR$EqualPercp)

attributes(Goldberg_callie$w14HHT13_2)
```



#Initial Model- PSAI Score vs. Household Division of Labor
```{r include=FALSE}

L1<- gls(w16PSAI_1~ HHT_HouseMean_1+ HHT_HouseMean_2 + as.factor(w14chgender_1)+ w14chcare_1 +w14chcare_2 +HHT_HouseMean_1*w14chcare_1+HHT_HouseMean_2*w14chcare_2,
         data=Goldberg_Callie_SR,
         correlation = corCompSymm(form=~1|famid),
         na.action = na.omit)
```

#Figure 1
```{r}
?ggplot
ggplot(Goldberg_Callie_SR, aes(x= HHT_HouseMean_1, y= w14chcare_1))+geom_jitter()
summary(L1)
```


#Model 2- PSAI Score vs. Parental makeup 
```{r}
names(select(Goldberg_callie, contains("sex")))
L2<- gls(w16PSAI_1~ as.factor(group)+ as.factor(w14chgender_1),
         data=Goldberg_Callie_SR,
         correlation = corCompSymm(form=~1|famid),
         na.action = na.omit)

summary(L2)
```

#Model 3
```{r}

favstats(w16PSAI_1 ~as.factor(group)|as.factor(w14chgender_1), data= Goldberg_Callie_SR)

L3<- gls(w16PSAI_1~as.factor(group) + HHT_HouseMean_1+ HHT_HouseMean_2+ as.factor(w14chgender_1),
         data=Goldberg_Callie_SR,
         correlation = corCompSymm(form=~1|famid),
         na.action = na.omit) 

summary(L3)

attributes(Goldberg_callie$group)
favstats= data.frame(favstats(w16PSAI_1 ~as.factor(group)|as.factor(w14chgender_1), data= Goldberg_Callie_SR))
View(favstats)
favstats$gender_group <- favstats$as.factor.w14chgender_1.

favstats_g <- fav
ggplot(favstats, aes(x= gender_group, y=mean))+geom_col()
```


```{r}
names(select(Goldberg_callie, w14chcare1_1:w14chcare25_1 ))

attributes(Goldberg_callie$w14chcare1_1)

Goldberg_Callie_SR$w14chcare_1<- rowMeans(select(Goldberg_Callie_SR, w14chcare1_1:w14chcare25_1), na.rm= TRUE)
Goldberg_Callie_SR$w14chcare_2<- rowMeans(select(Goldberg_Callie_SR, w14chcare1_2:w14chcare25_2), na.rm= TRUE)

```


```{r Figure 1}
#plot(L1)

ggplot(data = Goldberg_Callie_SR, aes(x =HHT_HouseMean, y= PAIst ))+
   geom_point()+
   labs(title="Gendered Play in Children vs. Household Divsion \n of Labour", y="PAI Score (with 0 being most Feminine \n & 5 being  Masculine Typed Play)", x="Household Tasks Distribution" )+
   geom_abline(slope=-0.9515, intercept=-3.1734, col="blue")
  

```

```{r Figure 2}
ggplot(data = Goldberg_Callie_SR, aes(x =EqualPercp, y= PAIst ))+
   geom_point()+
   labs(title="Gendered Play in Children vs. Equality of Household Divsion of Labour", 
    y="PAI Score (with 0 being most Feminine \n & 5  being  Masculine Typed Play)", 
    x="Equality in Division of Labor \n Household Tasks  (with 1 being equal and 0 being not equal)" )+
   geom_abline(slope=-1.3440, intercept=-6.0979 , col="blue")

```

```{r Figure 3}
#Intially graph does -1, 1 for sexor order, -1 corresponds to het & 1 corresponds to ss
ggplot(data = Goldberg_Callie_SR, aes(x =HHT_HouseMean, y= PAIst , color=as.factor(sexor)))+
   geom_point()+
   labs(title="Gendered Play in Children vs. Household Divsion \n of Labour", y="PAI Score (with 0 being most Feminine \n & 5 being  Masculine Typed Play)", x="Household Tasks Distribution", legend="Parent Sexual Orientation" )+
  geom_abline(slope=-0.8393 , intercept=-3.5837, col="black")+
    geom_abline(slope=-0.8393 , intercept=-3.5837+0.2331 , col="blue")+
  scale_color_discrete(name="Parent Sexual Orientation",labels=c("Heterosexual", "Same-Sex"))
#scale_color_manual(values=c("blue", "white"), labels= c("Heterosexual Parents", "Homosexual Parents"))



```
```{r Figure 3}
#Intially graph does -1, 1 for sexor order, -1 corresponds to het & 1 corresponds to ss
ggplot(data = Goldberg_Callie_SR, aes(x =HHT_HouseMean, y= PAIst , color=as.factor(sexor)))+
   geom_point()+
  facet_grid(~sexor, margins=TRUE)+
   labs(title="Gendered Play in Children vs. Household Divsion \n of Labour", y="PAI Score (with 0 being most Feminine \n & 5 being  Masculine Typed Play)", x="Household Tasks Distribution", legend="Parent Sexual Orientation" )+
  geom_abline(slope=-0.9515, intercept=-3.1734, col="blue")+
  scale_color_discrete(name="Parent Sexual Orientation",labels=c("Heterosexual", "Same-Sex"))
#scale_color_manual(values=c("blue", "white"), labels= c("Heterosexual Parents", "Homosexual Parents"))


```
#Main Results 
 Figure 1 through 3 are the anova tables for our diffent level of models. None showed statistically significant results. 
  If the there is no signifcant influance of sexual orentation on gender displa, with a b= 0.25, SE= .297, p= 0.4, and neither was the distruption of Household chores with a b= -0.951, SE= 1.45, and a p=.5. There possible flaws in our model that could lead to such a high value mainly that they are muilt-level as they should be with dyad

\newpage

# References


\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

