---
title             : "PSY/SDS 364: Resutls Write Up"
shorttitle        : "Measures and Descriptive Statistic"

author: 
  - name          : "Margret Perry"
    affiliation   : "1"
  - name          : "Callie Selvin"
    affliation    : "2"
  - name          : "Isabel Zamudio-Moore"
    affliation    : "3"
  
    corresponding : yes    # Define only one corresponding author
    address       : "Northampton, MA"
    email         : "izamudiomoore@smith.edu"

affiliation:
  - id            : "1"
    institution   : "Smith College"

author_note: >
  Smith College
  
keywords          : "Division of Labor, Gender Role Development, Preschool Activities Inventory"
wordcount         : "X"

bibliography      : ["MDSreferences.bib","r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r include = FALSE}
library(papaja)
library(mosaic)
library(psych)
```

```{r create_r-references}
r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "MDSreferences.bib")
```


```{r}
#install.packages("psych")
#install.packages("plyr")
library(psysds364data)
library(devtools)
library(tidyr)
library(mosaic)
library(dplyr)
library(ggplot2)
library(plyr)
```

```{r, include=FALSE}

Goldberg_callie_1<- Goldberg_callie_na%>%
  muta
test1<- gls()


```
# Dataset: Goldberg

# Question: How does the display of gender roles in children vary with the change in delegation of household responsibilities between parents?

#Analysis Strategy Section+Hypothesis

#Remind reaader of resrach question
Our resaerch seeks to look out the question of how the display of gender roles in children vary with the change in delegation of household responsibilities between parents?


2. Dyadic Data Analaysis
3. Take a figure of this.
4. Talk about data processing and how we
arrived at the model.

Data Processing

#ScaleScore



```{r}
data("Goldberg_callie")
Goldberg_Callie_2<- Goldberg_callie

```

#Scale Score
```{r}
Goldberg_Callie_SR<- Goldberg_Callie_2%>%
mutate(SR_PSAc1_1=0, SR_PSAc2_1=0, SR_PSAc3_1=0, SR_PSAc4_1=0, SR_PSAc5_1=0, SR_PSAc6_1=0,
SR_PSAa1_1=0, SR_PSAa2_1=0, SR_PSAa3_1=0, SR_PSAa4_1=0, SR_PSAa5_1=0, SR_PSAa6_1=0, SR_PSAa7_1=0, SR_PSAa8_1=0, SR_SR_PSAa9_1=0, SR_PSAa10_1=0, SR_PSAa11_1=0,
SR_PSAt1_1=0, SR_PSAt2_1=0, SR_PSAt3_1=0, SR_PSAt4_1=0, SR_PSAt5_1=0, SR_PSAt6_1=0, SR_PSAt7_1=0)

#Create binary variables for wether a specific variable has been recorded for Person 1
#Binary for character
Goldberg_Callie_SR$SR_PSAc1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac1_1), 1,0)

Goldberg_Callie_SR$SR_PSAc2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac2_1),1,0)

Goldberg_Callie_SR$SR_PSAc3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac3_1),1,0)

Goldberg_Callie_SR$SR_PSAc4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac4_1),1,0)

Goldberg_Callie_SR$SR_PSAc5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac5_1),1,0)

Goldberg_Callie_SR$SR_PSAc6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac6_1),1,0)

#Binary for activity
Goldberg_Callie_SR$SR_PSAa1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ1_1),1,0)

Goldberg_Callie_SR$SR_PSAa2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ2_1),1,0)

Goldberg_Callie_SR$SR_PSAa3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ3_1),1,0)

Goldberg_Callie_SR$SR_PSAa4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ4_1),1,0)

Goldberg_Callie_SR$SR_PSAa5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ5_1),1,0)


Goldberg_Callie_SR$SR_PSAa6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ6_1),1,0)

Goldberg_Callie_SR$SR_PSAa7_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ7_1),1,0)


Goldberg_Callie_SR$SR_PSAa8_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ8_1),1,0)


Goldberg_Callie_SR$SR_PSAa9_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ9_1),1,0)


Goldberg_Callie_SR$SR_PSAa10_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ10_1),1,0)

Goldberg_Callie_SR$SR_PSAa11_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ11_1),1,0)

Goldberg_Callie_SR$SR_PSAt1_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys1_1),1,0)

Goldberg_Callie_SR$SR_PSAt2_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys2_1),1,0)

Goldberg_Callie_SR$SR_PSAt3_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys3_1),1,0)

Goldberg_Callie_SR$SR_PSAt4_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys4_1),1,0)

Goldberg_Callie_SR$SR_PSAt5_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys5_1),1,0)

Goldberg_Callie_SR$SR_PSAt6_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys6_1),1,0)

Goldberg_Callie_SR$SR_PSAt7_1 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys7_1),1,0)

#SR_PSAc3=w16charac3_1,     SR_PSAc4= w16charac4_1, SR_PSAc1=w16charac5_1,     SR_PSAc6= w16charac6_1, 
 # SR_PSAc1=w16charac1_1)
#summary(Goldberg_Callie_SR$SR_PSAc1)
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI_1=SR_PSAc1_1+ SR_PSAc2_1+ SR_PSAc3_1+ SR_PSAc4_1+ SR_PSAc5_1+ SR_PSAc6_1+
SR_PSAa1_1+ SR_PSAa2_1+ SR_PSAa3_1+ SR_PSAa4_1+ SR_PSAa5_1+ SR_PSAa6_1+ SR_PSAa7_1+ SR_PSAa8_1, SR_PSAa9_1+ SR_PSAa10_1, SR_PSAa11_1+
SR_PSAt1_1+ SR_PSAt2_1, SR_PSAt3_1, SR_PSAt4_1, SR_PSAt5_1+ SR_PSAt6_1, SR_PSAt7_1)

```

#Scale Score
```{r}
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PSAc1_2=0, SR_PSAc2_2=0, SR_PSAc3_2=0, SR_PSAc4_2=0, SR_PSAc5_2=0, SR_PSAc6_2=0,
SR_PSAa1_2=0, SR_PSAa2_2=0, SR_PSAa3_2=0, SR_PSAa4_2=0, SR_PSAa5_2=0, SR_PSAa6_2=0, SR_PSAa7_2=0, SR_PSAa8_2=0, SR_PSAa9_2=0, SR_PSAa10_2=0, SR_PSAa11_2=0,
SR_PSAt2_2=0, SR_PSAt2_2=0, SR_PSAt3_2=0, SR_PSAt4_2=0, SR_PSAt5_2=0, SR_PSAt6_2=0, SR_PSAt7_2=0)

#Create binary variables for wether a specific variable has been recorded for Person 1
#Binary for character
Goldberg_Callie_SR$SR_PSAc1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac1_2), 1,0)

Goldberg_Callie_SR$SR_PSAc2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac2_2),1,0)

Goldberg_Callie_SR$SR_PSAc3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac3_2),1,0)

Goldberg_Callie_SR$SR_PSAc4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac4_2),1,0)

Goldberg_Callie_SR$SR_PSAc5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac5_2),1,0)

Goldberg_Callie_SR$SR_PSAc6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16charac6_2),1,0)

#Binary for activity
Goldberg_Callie_SR$SR_PSAa1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ1_2),1,0)

Goldberg_Callie_SR$SR_PSAa2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ2_2),1,0)

Goldberg_Callie_SR$SR_PSAa3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ3_2),1,0)

Goldberg_Callie_SR$SR_PSAa4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ4_2),1,0)

Goldberg_Callie_SR$SR_PSAa5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ5_2),1,0)


Goldberg_Callie_SR$SR_PSAa6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ6_2),1,0)

Goldberg_Callie_SR$SR_PSAa7_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ7_2),1,0)


Goldberg_Callie_SR$SR_PSAa8_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ8_2),1,0)


Goldberg_Callie_SR$SR_PSAa9_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ9_2),1,0)


Goldberg_Callie_SR$SR_PSAa10_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ10_2),1,0)

Goldberg_Callie_SR$SR_PSAa11_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16activ11_2),1,0)

Goldberg_Callie_SR$SR_PSAt1_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys1_2),1,0)

Goldberg_Callie_SR$SR_PSAt2_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys2_2),1,0)

Goldberg_Callie_SR$SR_PSAt3_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys3_2),1,0)

Goldberg_Callie_SR$SR_PSAt4_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys4_2),1,0)

Goldberg_Callie_SR$SR_PSAt5_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys5_2),1,0)

Goldberg_Callie_SR$SR_PSAt6_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys6_2),1,0)

Goldberg_Callie_SR$SR_PSAt7_2 <- 
ifelse(is.na(Goldberg_Callie_SR$w16toys7_2),1,0)

#SR_PSAc3=w16charac3_1,     SR_PSAc4= w16charac4_1, SR_PSAc1=w16charac5_1,     SR_PSAc6= w16charac6_1, 
 # SR_PSAc1=w16charac1_1)
#summary(Goldberg_Callie_SR$SR_PSAc1)
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI_2=SR_PSAc1_2+ SR_PSAc2_2+ SR_PSAc3_2+ SR_PSAc4_2+ SR_PSAc5_2+ SR_PSAc6_2+
SR_PSAa1_2+ SR_PSAa2_2+ SR_PSAa3_2+ SR_PSAa4_2+ SR_PSAa5_2+ SR_PSAa6_2+ SR_PSAa7_2+ SR_PSAa8_2, SR_PSAa9_2+ SR_PSAa10_2, SR_PSAa11_2+
SR_PSAt1_2+ SR_PSAt2_2, SR_PSAt3_2, SR_PSAt4_2, SR_PSAt5_2+ SR_PSAt6_2, SR_PSAt7_2)

```

```{r}
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
mutate(SR_PAI=SR_PAI_1+SR_PAI_2)

```


```{r}
ActNum<- 7+6+11
ActNum<- ActNum*2
CoupwOneP<- ActNum*0.01
CoupwTenP<- ActNum*0.05
CoupwFiveP<- ActNum*0.1


```

```{r}
Original<- nrow(Goldberg_Callie_SR)
```

```{r}
Goldberg_Callie_SR_10<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwTenP)

NumPartwTen<-nrow(Goldberg_Callie_SR_10)

Goldberg_Callie_SR_5<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwFiveP)

NumPartwFive<-nrow(Goldberg_Callie_SR_5)

Goldberg_Callie_SR_1<-Goldberg_Callie_SR%>%
  filter(SR_PAI>=CoupwOneP)

NumPartwOne<-nrow(Goldberg_Callie_SR_1)



```


```{r}
PartwTenPer<- NumPartwTen/Original
PartwTenPer

PartwFivePer<-  NumPartwFive/Original
PartwFivePer

PartwOnePer<- NumPartwOne/Original
PartwOnePer
```



In our data processing, it was decided that we would work with a scale score and would only exclude participants if the participant answered at least 5% of questions. This would only allow us to keep only a little over half of our paricipants in the study, `r printnum(PartwOnePer)` It was decided that regardless of the scale score partipants would be included in the study.



```{r}
#Call data
data("Goldberg_callie")

##sample code referance
attributes(Goldberg_callie$w16activ4_2)
names(select(Goldberg_callie, contains("sex")))
?Goldberg
attributes(Goldberg_callie$w16ra)
cortest<-corr.test(select(Goldberg_callie, w16activ1_2, w16activ2_2, w16activ3_2,w16activ4_2, w16activ5_2, w16activ6_2, w16activ7_2, w16activ8_2,w16activ9_2, w16activ10_2, w16activ11_2))$r
names(select(Goldberg_callie, contains("gender")))

attributes(Goldberg_callie$w16activ10_2)
attributes(Goldberg_callie$w16activ3_2)
```


To arrive at the model, we worked to standardize information based on gender and the age of the child working of the standardization models found by Garcia et al.

#Child Gender Data
```{r}
 summary(Goldberg_Callie_SR$w14chgender_1)
```

```{r}
names(select(Goldberg_callie, contains("chage")))
```

```{r}

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(w16chagemo=0)

AgeSubset<- Goldberg_Callie_SR%>%
  select(famid, partnum, w16chagemo_1,w16chagemo_2)

AgeMatrix<- as.matrix(AgeSubset)
AgeMatrixSub<- AgeMatrix[ ,3:4]
AgeMeans<- rowMeans(AgeMatrixSub)
head(AgeMatrixSub)
#View(AgeMeans)
AgeMatrix<-cbind(AgeMatrix, AgeMeans)
AgeMRejoin<-as.data.frame(AgeMatrix)
#View(AgeMatrix)
#View(AgeMRejoin)

Goldberg_Callie_SR<-join(AgeMRejoin,Goldberg_Callie_SR)
#View(Rejoin)

```

```{r}
 summary(Goldberg_Callie_SR$w14chgender_1)
```

```{r}
names(select(Goldberg_callie, contains("chage")))
```

```{r}

Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(PAIfin=0)

```
















//Standardization
#RETURN TO!
```{r}
Goldberg_Callie_SR<- Goldberg_Callie_SR%>%
  mutate(PAIst=0)

Goldberg_Callie_SR$PAIst<- if_else(Goldberg_Callie_SR$w14chgender_1==-1,
            Goldberg_Callie_SR$PAIfin*1.075-w16chagemo*0.177+0.088 )

Goldberg_Callie_SR$PAIst<- if_else(Goldberg_Callie_SR$w14chgender_1==1,
                    PAIfin*1.026-w16chagemo*0.218+8.33)

```

```{r}
#Get the mean of all tasks


```
#Main Result Section
1. Write about coeficents.
2. Figure
3. EDA

*pvalue,SE use three decimal points
*coef use two decimal points

round(coef,#decminal)



